The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-22 paper.tex
update

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                                             & Description                               & Value                                & Reference                       \\ \midrule
{\bf ISM Disk }                                       &                                           &                                      &                                 \\
$z_{0}$                                               & Scale height of disk                      & 100 pc                               & \citet{peak-ism-density}        \\
$T_{\text{\text{disk}}}$                              & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}          \\
$\rho_{\text{disk}}^{\text{peak}}$                    & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}          \\
$T_{\text{\text{c}}}$                                 & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   & \multicolumn{1}{c}{''}          \\
$k_{\text{min}}$                                      & Cutoff wave number                        & 375.0                                & \multicolumn{1}{c}{''}          \\
$\mu$                                                 & Mean of number density                    & 1.3 $\text{cm}^{-3}$                 & \citet{Wagner2012}              \\
$\sigma$                                              & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 & \multicolumn{1}{c}{''}          \\
$\beta$                                               & Power law index                           & -5/3                                 & \multicolumn{1}{c}{''}          \\ \hline
{\bf Atmosphere }                                     &                                           &                                      &                                 \\
$T_{\text{\text{atmp}}}$                              & Temperature of atmosphere                 & $10^{6}$ K                           & \citet{temperature-MW}          \\ \hline
{\bf Static stellar potential }                       &                                           &                                      &                                 \\
$\sigma_{\text{bulge}}$                               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citet{velocity-dispersion-MW}  \\
$\rho_{\text{bulge}}^{\text{peak}}$                   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &                                 \\ \hline
{\bf Static dark halo potential }                     &                                           &                                      &                                 \\
$v_{\text{halo}}$                                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citet{Johnston1995}            \\
$d_{\text{h}}$                                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}          \\ \midrule
\end{tabular}
\end{table*}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                                             & Description                               & Value                                & Reference                       \\ \midrule
{\bf ISM Disk }                                       &                                           &                                      &                                 \\
$z_{0}$                                               & Scale height of disk                      & 100 pc                               & \citet{peak-ism-density}        \\
$T_{\text{\text{disk}}}$                              & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}          \\
$\rho_{\text{disk}}^{\text{peak}}$                    & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}          \\
$T_{\text{\text{c}}}$                                 & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   & \multicolumn{1}{c}{''}          \\
$k_{\text{min}}$                                      & Cutoff wave number                        & 375.0                                & \multicolumn{1}{c}{''}          \\
$\mu$                                                 & Mean of number density                    & 1.0 $\text{cm}^{-3}$                 & \citet{Wagner2012}              \\
$\sigma$                                              & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 & \multicolumn{1}{c}{''}          \\
$\beta$                                               & Power law index                           & -5/3                                 & \multicolumn{1}{c}{''}          \\ \hline
{\bf Atmosphere }                                     &                                           &                                      &                                 \\
$T_{\text{\text{atmp}}}$                              & Temperature of atmosphere                 & $10^{6}$ K                           & \citet{temperature-MW}          \\ \hline
{\bf Static stellar potential }                       &                                           &                                      &                                 \\
$\sigma_{\text{bulge}}$                               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citet{velocity-dispersion-MW}  \\
$\rho_{\text{bulge}}^{\text{peak}}$                   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &                                 \\ \hline
{\bf Static dark halo potential }                     &                                           &                                      &                                 \\
$v_{\text{halo}}$                                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citet{Johnston1995}            \\
$d_{\text{h}}$                                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}          \\ \midrule
\end{tabular}
\end{table*}
